---
title: "Tenzin Lhamo's Dashboard for DACSS Data Visualization"
bibliography: library.bib
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard) # always
library(ggplot2)
library(scales)
```

## Intro {.sidebar}

Preparing the dashboard based on the instructions given at @magallanes_reyes_data_2022, and aden-buie_flexdashboard_2024.

### References
<div id="refs"></div>


To organize your Flexdashboard into tabs rather than all sections being on one page, you can structure your R Markdown using Level 2 headers (##) to define separate tabs. This will ensure that each tab occupies the full space, making your plots appear larger and easier to read.

Updated Layout for Tabs in Flexdashboard:
Here’s how you can revise your layout:

yaml
Copy
Edit
---
title: "Tenzin Lhamo's Dashboard for DACSS Data Visualization"
bibliography: library.bib
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---
R Markdown Body:
Use Level 2 Headers (##) for tabs and organize your plots accordingly:

markdown
Copy
Edit
## Intro {.sidebar}

Preparing the dashboard based on the instructions given at @magallanes_reyes_data_2022, and aden-buie_flexdashboard_2024.

### References
<div id="refs"></div>

---

## Deliverable 1 Plot <!-- Suburb Locale Distribution Barplot -->

```{r, cache = FALSE, fig.width = 10, fig.height = 6}
#load the saved plot from the RDS file
plot_data = readRDS('newPlot.rds')
newPlot = plot_data$plot
LABELS = plot_data$labels
print(newPlot)
```

## Deliverable 2 Plot <!-- MA State Police Arrest Type-Age Barplot -->

```{r, cache = FALSE, fig.width = 10, fig.height = 6}
plot2 = readRDS('plot2.rds')
print(plot2)
```
